Use Of Jigsaw Puzzle Solving Algorithms In The Real World

### 2023-10-01 LaTeX_paper/paper.tex
finish paper V1

@@

\section{The Objective Of This Paper}
After reading some of the previous literature for this problem, some conclusions could be drawn:
The problem of ``digital'' jigsaw puzzle has been solved many times, and is already well optimized.\newline
On the other hand, the problem of ``real world'' jigsaw puzzle has mostly been ignored
by the academic community.\newline
The first objective for this paper is to fill this void, and been the first formal paper to analyze the
``real world'' jigsaw puzzle problem.\newline
The second objective of this paper is to use the research that has been done to create a labeling tool.\newline
The reason behind this objective is that the biggest challenge for real world puzzles is creating a
reliable comparator~\ref{document:comparator}. That can deal with all the noisy 
images you get from the real world.\newline
It is easy to see how a machine learning based comparator would probably be the best solution, 
but this has some problems, in fact having to manually scan and label thousands of individual puzzle
pieces to train the model would take ages.
Instead an automatic tool would be abel to scan a small $4\times4$ puzzle in one shot,
solve it, and return the labeled data in just a couple minutes.

@@

\subsubsection{Definitions}
This set of definitions are useful to better understand the next section:

@@

\section{The Solver}
The Solver that has been created is not the main focus of this paper,
and cannot be considered state-of-the-art if compared with the current best
digital puzzle solver. But can probably be considered so if compared with current
``real world'' puzzle Solvers.z

@@

\subsubsection{Combining four objects}

@@

>>>>

\usepackage{multirow}

@@

\section{The Objective Of This Paper}\label{document:objective}
After reading some of the previous literature for this problem, some conclusions could be drawn:
The problem of ``digital'' jigsaw puzzle has been solved many times, and is already well optimized.\newline
On the other hand, the problem of ``real world'' jigsaw puzzle has mostly been ignored
by the academic community.\newline
The first objective for this paper is to fill this void, and been the first formal paper to analyze the
``real world'' jigsaw puzzle problem.\newline
The second objective of this paper is to use the research that has been done to create a labeling tool.\newline
The reason behind this objective is that the biggest challenge for real world puzzles is creating a
reliable comparator~\ref{document:comparator}. That can deal with all the noisy 
images you get from the real world.\newline
It is easy to see how a machine learning based comparator would probably be the best solution, 
but this has some problems, in fact having to manually scan and label thousands of individual puzzle
pieces to train the model would take ages.
Instead an automatic tool would be abel to scan a small $4\times4$ puzzle in one shot,
solve it, and return the labeled data in just a couple minutes.

@@

\subsubsection{Definitions}\label{document:proof_definitions}
This set of definitions are useful to better understand the next section:

@@

\section{The Solver}\label{document:my_solver}
The Solver that has been created is not the main focus of this paper,
and cannot be considered state-of-the-art if compared with the current best
digital puzzle solver. But can probably be considered so if compared with current
``real world'' puzzle Solvers.z

@@

\subsubsection{Combining four objects}\label{document:combining_four_objects}

@@

\section{Testing Results}

In this section the solver that has been proposed by this paper will be tested.
This test will serve two purposes:
Understanding the performance and limitations of the proposed algorithm
Been able to test the same algorithm with both digital, and real world jigsaw puzzles, to understand the differences between the two.

\subsection{Setup}
The test sample consist in 5 different puzzle:
\begin{itemize}
  \item a 4x4 real world puzzle
  \item a 8x8 real world puzzle
  \item a 4x4 digital puzzle
  \item a 8x8 digital puzzle
  \item a 16x16 digital puzzle
\end{itemize}
The real world puzzles have been obtained with a printer’s scanner,
and the digital puzzles have been obtained from \url{https://puzzle.telegnom.org/}.\newline
The constants MIN\_SHORE\_SINGLE\_SIDE and MIN\_SHORE\_PIECE\_GROUP mentioned in section
\ref{document:combining_four_objects} were set at different values
depending on the nature of the puzzle (real or digital).\newline
The test has been performed on a ryzen 5 5600 CPU with 16 GB of RAM.
The time measured in the test does not include the execution time of the Comparator
\ref{document:my_comparator}, but only the one of the Solver~\ref{document:my_solver}.

\subsection{Results}

\begin{table}[H]
  \centering
  \begin{tabular}{
  >{\columncolor[HTML]{D9EAD3}}c 
  >{\columncolor[HTML]{D0E0E3}}c 
  >{\columncolor[HTML]{E6B8AF}}c 
  >{\columncolor[HTML]{FCE5CD}}c }
  \cellcolor[HTML]{B6D7A8} &
    \cellcolor[HTML]{A2C4C9} &
    \multicolumn{2}{c}{\cellcolor[HTML]{EA9999}Execution time {[}s{]}} \\
  \multirow{-2}{*}{\cellcolor[HTML]{B6D7A8}Size} &
    \multirow{-2}{*}{\cellcolor[HTML]{A2C4C9}Pieces} &
    \cellcolor[HTML]{DD7E6B}Digital puzzle &
    \cellcolor[HTML]{F9CB9C}Real Puzzle \\
  4x4   & 16  & 4   & 59   \\
  8x8   & 64  & 30  & 2851 \\
  16X16 & 256 & 377 & N/A 
  \end{tabular}
\end{table}

\subsection{Accuracy}
It is important to note that the project does not have a way to evaluate the accuracy
of the results automatically. But the accuracy for the two real world puzzles
has been asserted manually. And both of them are 100\% correct.

\subsection{Analysis}

This paper has claimed from the start that real world puzzles were harder than digital ones.
Some intuitive explanations were given to justify this claim,
but a formal proof has never been given.
This test finally proves the claim, by showing that the same algorithm can have vastly
different time performances depending on the accuracy of the input data.

It is fair to say that the performance of the algorithm are not amazing,
but they are good enough to achieve the objective of this paper \ref{document:objective}.
It is also worth remembering that the problem itself is extremely complex.
Using the formula introduced in section \ref{document:proof_definitions} we can calculate that a 64 piece puzzle,
like the one that has been solved before, has approximately \(4 \cdot 10^{127}\) possible combinations.
\[C = N! \cdot 4^N =  64! \cdot 4^{64} \approx 4.32 \cdot 10^{127}\]
